A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-15 doc/draft-01-stokes/03analysis.tex
spell check

Before proving the main theorems, we require a number
of uniqueness results for oscillatory Stokes boundary
value problems.
%
To prove the uniqueness results, we follow the 
structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
for the scalar Helmholtz equation.
%
While uniqueness results for interior Dirchilet,
Neumann, and impedance problems follow from energy
considerations and compactness arguments, the proofs
for the uniqueness of exterior problems are more
involved.
%
In particular, the exterior problems are only 
well-posed after imposing an appropriate radiation
condition.
%
We formulate well-posed boundary value problems 
for both interior and exterior domains with
Dirichlet, Neumann and impedance boundary
conditions and present uniqueness results for
each.

@@

\begin{thrm}
  Let $\Omega$ be a bounded domain and suppose that
  $\Re(k),\Im (k) > 0$. Then the interior
  impendence problem has a unique solution.
\end{thrm}
\begin{proof}
  Plugging $\bt = i\eta \bu$ in~\cref{eq:greenlike}
  and taking the imaginary part, we get
  \begin{equation}
   2 \Re{(k)} \Im{(k)} \int_{\Omega} |\bu|^2\, dV + 2\Re{(\eta)} \int_{\Gamma}
   |\bu|^2 \, dS = 0 \, ,
  \end{equation}
  from which it is is clear that $\bu \equiv 0$, since
  $\Re{(\eta)}, \Re{(k)}, \Im{(k)} > 0$.
\end{proof}

@@

To show that $\bmu=0$ on
$\Gamma_{j}$, we observe that $\bu$ is also a
solution to the oscillatory Stokes equation in each
of the obstacles $\Omega_{j}$.
Using the jump conditions in~\cref{lem:jump-conds},
we get that $\bt^{+} = 2i\eta \bmu$ and $\bu^{+} = -2\bmu$.
However, the normal is inward pointing inside $\Omega_{j}$
on the boundary $\Gamma_{j}$. 
If we revert back to the normal being defined as 
an outward normal to $\Omega_{j}$, then
the boundary conditions on $\Gamma_{j}$ 
is $\bt - i \eta \bu = 0$. 
From the uniqueness of solutions to the interior 
impedance problem, we conlcude that $\bu \equiv 0$
in $\Omega_{j}$, which in particular implies
that $2\bmu = \bu^{-}-\bu^{+} = 0$ for $\xx \in \Gamma_{j}$,
$j=1,2,\ldots m$.
Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is
invertible when $k^2$ is not a Dirichlet eigenvalue
for the Stokes equation on $\Omega$.

>>>>

Before proving the main theorems, we require a number
of uniqueness results for oscillatory Stokes boundary
value problems.
%
To prove the uniqueness results, we follow the 
structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
for the scalar Helmholtz equation.
%
While uniqueness results for interior Dirichlet,
Neumann, and impedance problems follow from energy
considerations and compactness arguments, the proofs
for the uniqueness of exterior problems are more
involved.
%
In particular, the exterior problems are only 
well-posed after imposing an appropriate radiation
condition.
%
We formulate well-posed boundary value problems 
for both interior and exterior domains with
Dirichlet, Neumann and impedance boundary
conditions and present uniqueness results for
each.

@@

\begin{thrm}
  Let $\Omega$ be a bounded domain and suppose that
  $\Re(k),\Im (k) > 0$. Then the interior
  impedance problem has a unique solution.
\end{thrm}
\begin{proof}
  Plugging $\bt = i\eta \bu$ in~\cref{eq:greenlike}
  and taking the imaginary part, we get
  \begin{equation}
   2 \Re{(k)} \Im{(k)} \int_{\Omega} |\bu|^2\, dV + 2\Re{(\eta)} \int_{\Gamma}
   |\bu|^2 \, dS = 0 \, ,
  \end{equation}
  from which it is is clear that $\bu \equiv 0$, since
  $\Re{(\eta)}, \Re{(k)}, \Im{(k)} > 0$.
\end{proof}

@@

To show that $\bmu=0$ on
$\Gamma_{j}$, we observe that $\bu$ is also a
solution to the oscillatory Stokes equation in each
of the obstacles $\Omega_{j}$.
Using the jump conditions in~\cref{lem:jump-conds},
we get that $\bt^{+} = 2i\eta \bmu$ and $\bu^{+} = -2\bmu$.
However, the normal is inward pointing inside $\Omega_{j}$
on the boundary $\Gamma_{j}$. 
If we revert back to the normal being defined as 
an outward normal to $\Omega_{j}$, then
the boundary conditions on $\Gamma_{j}$ 
is $\bt - i \eta \bu = 0$. 
From the uniqueness of solutions to the interior 
impedance problem, we conclude that $\bu \equiv 0$
in $\Omega_{j}$, which in particular implies
that $2\bmu = \bu^{-}-\bu^{+} = 0$ for $\xx \in \Gamma_{j}$,
$j=1,2,\ldots m$.
Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is
invertible when $k^2$ is not a Dirichlet eigenvalue
for the Stokes equation on $\Omega$.

### 2019-04-15 doc/draft-01-stokes/04numerical.tex
spell check

The compressed representation also allows
for fast applications of the system matrix,
its transpose, the inverse of the system
matrix, and the inverse transpose to
vectors.
%
In particular, this allows us to estimate the
smallest singular values by performing
randomized subspace iteration, see
\cite[Algorithm 4.4]{halko2011finding},
on the inverse operator.
%
Below, we use the smallest singular value
as a measure of the quality of the
eigenvalues found by approximating the
roots of the determinant.
%
We also evaluate the second smallest singular
value if the root finding precedure suggests a
possible double root.

@@

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Note that $N^{-20}$ is the expected order of
convergence for Generalized Gaussiuan quadratures for weakly 
singular integrals.
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.

>>>>

The compressed representation also allows
for fast applications of the system matrix,
its transpose, the inverse of the system
matrix, and the inverse transpose to
vectors.
%
In particular, this allows us to estimate the
smallest singular values by performing
randomized subspace iteration, see
\cite[Algorithm 4.4]{halko2011finding},
on the inverse operator.
%
Below, we use the smallest singular value
as a measure of the quality of the
eigenvalues found by approximating the
roots of the determinant.
%
We also evaluate the second smallest singular
value if the root finding procedure suggests a
possible double root.

@@

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Note that $N^{-20}$ is the expected order of
convergence for Generalized Gaussian quadrature for weakly 
singular integrals.
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.
